\section{Interfaces}
In this section we specify interfaces for all objects in the software model, as seen in figure \ref{fig:softwareArchitecture}. This includes the API-objects, which are intended to abstract from hardware specific  information like the calibration of sensors and filtering out incorrect measurements from the raw data. 

\todo{Probably do this inside a draw.io diagram}

\subsection{API classes}
They all require a calibrate-method, which is called whenever the bus starts in order to ensure the sensors work as intended. 

\unsure{HOW DOES THIS WORK IN RELATION TO RTS and .oil files? How do we split all these functions into multiple tasks that can be scheduled using .oil files?}

\begin{description}
    \item [Motor]
    FindCentrum(); ???? Does this make sense for the motor for speed?
    SetRotation(int rpm, enum direction);
    
    \todo{Do I need an API for turning as well? or can I combine speed and turning in one?}
    
    The enum contains the choices: forwards and backwards. Rpm abbreviates rotations per minute.
    
    \item [LightSensor]
    \item [SoundSignaling]
    \item [Bluetooth]
    \item [Ultrasonic]
    \item [CamDetectObjects]
    \item [CamLineTracking]
\end{description}

\subsection{Other classes}
\subsection{API-objects}
\begin{description}
    \item [Signaling]
    void StartManeuvre(enum maneuvre);
    void EndManeuvre(enum maneuvre);
    enum CurrentManeuvre;
    
    The enum contains the choices: stopped, straight, turnLeft, turnRight, brake, reverse and emergency. 
\end{description}

\subsection{Component classes}
\begin{description}
    \item [Driving]
    void TurnDegrees(int targetDegrees, enum direction);
    void TurnDegrees(int degrees, enum inDirection);
    void SetSpeed(int targetKmHr, bool smooth);
    void IncreaseSpeed(int kmHr, bool smooth);
    void ReduceSpeed(int kmHr, bool smooth);
    void Stop(bool smooth);
    
    enum currentDirection;
    int currentTurn;
    int MaxSpeed;
    int CurrentSpeed;

    The enum contains the choices: left and right. The bool "smooth" decides whether the speed increase/decrease is gradual or not. 
    
    \item [Maneuvre]
    \item [StayWithinLane]
    \item [CruiseControl]
    \item [ObstacleAvoidance]
    \item [SpeedZoneControl]
    \item [StopButton]
    \item [DetectBusStop]
\end{description}