\section{Brainstorm}

A brainstorm was made in order to find the potential functionality an autonomous bus could implement in the context of the problem statement. The results of the brainstorm and a short description of each feature is shown below. 

\begin{description}
\item [Follow Track]
The general idea here is to drive within a set of boundaries, like road markings.

\item[Stop Button]
A way to signal the bus that some passengers want to get off at the next bus stop.\unsure{source needed?}

\item[Detect Bus Stop]
Detection of a marker or a sign that indicates where the bus stop is located.

\item[Switch Lanes]
This functionality allows the bus to switch into and out of the lane in which the bus stop is located, and also allows overtaking other vehicles. 

\item[Overtake]
Allows the bus to overtake a stopped or slow vehicle. 

\item[Speed Limiter]
A limiter that enforces a designated speed, making sure that it speeds up/slows down to match the speed limit.

\item[Cruise Control]
Staying behind a moving object without constantly accelerating and braking, thereby providing a smooth journey.

\item[Detecting Obstacles]
The ability to detect obstacles, such that it can brake or manoeuvre to prevent crashes.

\item[Door]
Controlling one or multiple doors to allow passengers to get on and off the bus.

\item[Intersections]
An intersection is a regular occurrence in the pre-existing infrastructure; it is therefore useful for the bus to be able to navigate them, whilst following traffic regulations.

\item[Roundabouts]
Like intersections, roundabouts are found in pre-existing infrastructures.

\item[Passenger Limit]
As per fire safety rules, only a set amount of passengers are allowed within any certain space at time. To conform to these rules, there should be some system that counts the passengers entering and leaving the bus.

\item[Transformer Bus]
Being able to combine or split buses allows for more flexibility in regards to making sure there's always sufficient space on the buses, which may vary for each route. 

\item[Dark Sensor]
Power can be saved if the bus only turns on the headlights when they are needed.\info{Isn't it illegal to have the lights turned off?}

\end{description}

%\unsure{A brainstorm was made based on our problem statement, to find all the potential useful functionality}












