\section{Future Work}

\subsection{Prevent wiggling of the bus}
 Placing the center of gravity much lower could have prevented some of the wiggling in the bus. However, to fully eliminate the wiggling, the bus would have to be built out of materials that are more stable and less flexible than LEGO.
 
 \subsection{Another driving algorithm}
 As mentioned in subsection \ref{pingpong}, the algorithm was not ideal in the long term. To prevent the bus from constantly turning left and right another algorithm would have to be used.
 This other algorithm would have to make the bus stay in the middle of the road, whilst making smooth turns to stay in the middle. Making an algorithm do this would however require knowledge about the positions of both sides of the road compared to the placement of the bus, and it would also require knowledge of how the road curves a good bit ahead of the bus. It is not possible to get the needed knowledge with the current camera setup. Either a different camera can be used, or potentially several cameras will have to be used. 
 
 \subsection{Building the bus from another material}
Currently the bus is made out of LEGO. building the bus out of LEGO is fast, and we could thus make different iterations of the bus at a fast pace, and change things on the bus without to much trouble. However, LEGO is very flexible, and the parts easily come apart. This makes the bus unstable, and sometimes parts can fall off that then needs to be put back on it. If instead the bus would be made out of a stronger material, then the bus would be far stronger, and less likely to break.
 